---
title: "LivTransplantEvolutionVignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{LivTransplantEvolutionVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval=FALSE}
library(LivTransplantEvolution)
```

## Introduction

`LivTransplantEvolution` is an R package that calculates and visualizes MELD, 
MELDna and MELD3.0 liver transplantation relevant risk scores
The package was developed on `R version 4.3.1 (2023-06-16)` on a Mac platform
To download **LivTransplantEvolution**, use the following commands:

```{r, eval=FALSE}
require("devtools")
devtools::install_github("Mouaid-Alim/LivTransplantEvolution", build_vignettes = TRUE)
library("LivTransplantEvolution")
```
To list all sample functions available in the package:
```{r, eval=FALSE}
ls("package:LivTransplantEvolution")
```

### Minimal requirements
You will need to have dataset with 

## Application
```{r, eval=FALSE}
library("LivTransplantEvolution")
?LivTransplantEvolution::calcMELDna
```

### Refernces

Bibliography

1.
Potosek, J., Curry, M., Buss, M. & Chittenden, E. Integration of palliative care in end-stage liver disease and liver transplantation. J. Palliat. Med. 17, 1271–1277 (2014).
2.
Summary statistics on organ transplants, wait-lists and donors. Cihi.ca https://www.cihi.ca/en/summary-statistics-on-organ-transplants-wait-lists-and-donors.
3.
Kwong, A. J. et al. OPTN/SRTR 2019 annual data report: Liver. Am. J. Transplant 21 Suppl 2, 208–315 (2021).
4.
Kamath, P. et al. A model to predict survival in patients with end-stage liver disease. Gastroenterology 120, A76–A77 (2001).
5.
Biggins, S. W. et al. Serum sodium predicts mortality in patients listed for liver transplantation. Hepatology 41, 32–39 (2005).
6.
Kim, W. R. et al. MELD 3.0: The model for end-Stage Liver Disease updated for the modern era. Gastroenterology 161, 1887-1895.e4 (2021).
7.
Liver transplant risk stratification. R-project.org https://cran.r-project.org/web/packages/transplantr/vignettes/liver_recipient_scoring.html.
8.
UCI Machine Learning. Indian Liver Patient Records. (2017).



